---
title: "Network Analysis - Twitter API - CNN"
output: html_document
---
```{r, echo=FALSE, cache=FALSE}
options(width = 200)
```
___
#### *Authors:* Ronit Yoari & Orel Swisa  
#### *Date*: May 3, 2016  
#### *The API Dataset based [Twitter](https://twitter.com) - Connect Orel_Swisa Twitter account *  
___
## *Data Description*
- This report provide detailed **hashtag** data from twitter about **CNN**, which took place on April 27, 2016.  
- The statistics relate only to tweets that contain the **CNN** hashtag.  

___
### *Data Example - Reading first data records*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
library("downloader")
library(twitteR)
library(tm)

# Twitter credentials
consumer_key <- "sjqXRKHfR2rD5VSPlYyscGTv1"
consumer_secret <- "fwB8pwlkc9K1YnrdKHt7pyZN0WzgsHiAoKUJJ9VpxCsoLKilWe"
access_token <- "1493511710-wmaNFnHNyn2FbutPkHCCwq61XOqYyuO7ODh4nsf"
access_secret <- "hpV8u6PCmH2eJUPbkUnKHPjgvTtPb5FnfUal64AM9phuR"

folder<-"rdatammining.Rdata.gz"
if(!file.exists(folder)){
  # Connect Twitter account
  sig <- twitteR::setup_twitter_oauth(consumer_key , consumer_secret, access_token, access_secret)
  # retrieve the first 100 tweets (or all tweets if fewer than 100)
  # from the user timeline of @rdatammining
  # rdmTweets <- userTimeline("cnn", n=1000)
  # get 500 tweets with the hashtag #cnn 
  cnn <- searchTwitter("@cnn", n = 1000 ,since = '2016-04-27 00:00', until = '2016-04-28 00:00')
  save(cnn, file=folder, compress=TRUE)
} else{
  load(folder)
}
head(cnn)
# Get the Date
dateAPI <- date()
dateAPI
```
```{r, include=FALSE,echo=FALSE}

data_mining_CNN <- twListToDF(cnn)
# Remove stop words :
data_mining_CNN2 = stringr::str_replace_all(data_mining_CNN$text,"[^[:graph:]]", " ")
# get the body of CNN hashtag
data_mining_corpus_CNN = tm::Corpus(VectorSource(data_mining_CNN2))
cnn_dtm = TermDocumentMatrix(data_mining_corpus_CNN, control = list(minWordLength = 4, removePunctuation=TRUE, stopwords = c(stopwords('english')), removeNumbers=TRUE,tolower=TRUE,stripWhitespace=TRUE))
te<-inspect(cnn_dtm)
termsMet1 <- te %*% t(te)
```

___  
### *Network analysis of tweets that contain the hashtag **CNN***  
#### Containing the following words:  
- ***USA Politicians*** : Obama, Hastert, Fiorina, Donald Trump, Bernie Sanders, Ted Cruz, Kasich, Hillary Clinton.  
- ***Sports News*** : Madrid, Atletico. 
```{r,echo=FALSE,message=FALSE}
library(igraph)
terms<-c('trump','donald','hillary', 'clinton', 'ted', 'cruz','obama','bernie','fiorina','sanders','indiana','madrid','atletico', 'hastert','sarah', 'palin','kasich')
termsMet<-termsMet1[terms,terms]
g <- graph.adjacency(termsMet, weighted=TRUE, mode = 'undirecte')
g <- set.edge.attribute(g, "weight", value=runif(ecount(g)))
g <- simplify(g)
```
### *Vertices*
```{r,echo=FALSE, message=FALSE}
V(g)$name
```
### *Edges*
```{r,echo=FALSE, message=FALSE}
E(g)
```
### *Summary*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
summary(g)
```
___
## *Centrality*
___
### *i. Betweeness* 
```{r,echo=FALSE}
btw <- betweenness(g) 
# rescale values to match the elements of a color vector 
btw.score <- round( (btw - min(btw)) * length(btw) / max(btw) ) + 1 
# create color vector, use rev to make red "hot" 
btw.colors <- rev(heat.colors(max(btw.score))) 
V(g)$color <- btw.colors[ btw.score ] 
g$layout <- layout.fruchterman.reingold(g)
plot(g)
which.max(btw)
max(btw)
```
___
### *ii. Closeness* 
```{r,echo=FALSE}
clo <- closeness(g) 
# rescale values to match the elements of a color vector 
clo.score <- round( (clo - min(clo)) * length(clo) / max(clo) ) + 1 
# create color vector, use rev to make red "hot" 
clo.colors <- rev(heat.colors(max(clo.score))) 
V(g)$color <- clo.colors[ clo.score ] 
plot(g)
which.max(clo)
max(clo)
```
___
### *iii. Eigencetor*
```{r,echo=FALSE}
temp <- eigen_centrality(g) 
evc<-temp$vector
# rescale values to match the elements of a color vector 
evc.score <- round( (evc - min(evc)) * length(evc) / max(evc) ) + 1 
# create color vector, use rev to make red "hot" 
evc.colors <- rev(heat.colors(max(evc.score))) 
V(g)$color <- evc.colors[ evc.score ] 
plot(g)
which.max(evc)
max(evc)
```
___
## *Identifying communities*
___
```{r,echo=FALSE,message=FALSE}
# Remove self-loops is exist
greyAnatomy <- simplify(g)
# Set seed (for layout) - so it won't be randomal
set.seed(200)
```
### *i. Zachary's algorithm*  
#### *The graph shown below describes the distribution of vertices communities, by color depending, according to **Zachary's algorithm***  
```{r,echo=FALSE,warning=FALSE,message=FALSE}
# Community strucure via short random walks
fc <- walktrap.community(greyAnatomy)
memb<-membership(fc)
lay <- layout.fruchterman.reingold(greyAnatomy)
plot(greyAnatomy, layout=lay, vertex.size=5, vertex.label=NA, vertex.color=memb+1, asp=FALSE)
```
  
#### *The number of the communities according to **Zachary's algorithm** is:* 
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(memb)
```
#### *The graph below shows the **distribution** of members in communities*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
membTable <- table(memb)
barplot(membTable, col=terrain.colors(7) , main="Bar plot for Number of Members\nVS\nCommunity", 
  	xlab="#Community", ylab = "Number of Members")
memb
```
  
#### *Modularity*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
fc$modularity
```
#### *Which one had the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
# get the max modularity for this graph:
which.max(fc$modularity)
```
#### *What the value of the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(fc$modularity)
```
___
### *ii. Second Algorithm - Girvan-Newman community detection algorithm*  
#### *The graph shown below describes the distribution of vertices communities, by color depending, according to **Girvan-Newman algorithm***  
```{r,echo=FALSE,warning=FALSE,message=FALSE}
fc <- edge.betweenness.community(greyAnatomy)
memb<-membership(fc)
plot(greyAnatomy, layout=lay, vertex.size=5, vertex.label=NA, vertex.color=memb+1, asp=FALSE)
```
  
#### *The number of the communities according to **Girvan-Newman** is:* 
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(memb)
```
#### *The graph below shows the **distribution** of members in communities*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
membTable <- table(memb)
barplot(membTable, col=terrain.colors(7) , main="Bar plot for Number of Members\nVS\nCommunity", 
  	xlab="#Community", ylab = "Number of Members")
memb
```  
#### *Modularity*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
fc$modularity
```
#### *Which one had the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
# get the max modularity for this graph:
which.max(fc$modularity)
```
#### *What the value of the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(fc$modularity)
```